Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-24 src/2.GenericProgramming.tex
Formatting change.

\begin{figure}[h]
\begin{Verbatim}[frame=leftline]
Constrained Semantics: memory allocations, memory movement, parallel kernels
Parallel Paradigms: patterns, tasks
Expression: language 
Concern: prescriptive, descriptive
\end{Verbatim}
\caption{Semantic capture - a set of constrained semantics, parallel paradigms, expression and concern define key properties a parallel programming model.}
\label{figSemCapture}
\end{figure}

>>>>

\begin{figure}[h]
\begin{Verbatim}[frame=leftline]
Constrained Semantics: memory allocations, 
memory movement, execution parameters
Parallel Paradigms: patterns, tasks
Expression: language 
Concern: prescriptive, descriptive
\end{Verbatim}
\caption{Semantic capture - a set of constrained semantics, parallel paradigms, expression and concern define key properties a parallel programming model.}
\label{figSemCapture}
\end{figure}
